### 2015-12-09 WRITEUP/Obs.tex
restructured GILDAS scripts, add draft for obs. section

For both tracks, the nearby radio quasar J1310+323 was observed every 15 minutes for
pointing, amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator. J1337$-$129 and 3C273 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\sim

@@

The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the upper sideband image cube. The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 208.3 MHz (corresponding to 687 km s$^{-1}$). % one bin is 83.195 km s$^{-1}$
The continuum image is created by
averaging over all the line-free channels ($\nu_{\rm cont}\sim$90.7 GHz). This yields a synthesized clean beam size of 3\farcs5 $\times$ 3\farcs0 and an rms noise of 0.24 mJy beam$^{-1}$.

>>>>

For both tracks, the nearby radio quasar J1310+323 was observed every 15 minutes for
pointing, amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator. J1337$-$129 and 3C273 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the upper sideband image cube. The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 208.3 MHz (corresponding to 687 km s$^{-1}$). % one bin is 83.195 km s$^{-1}$
The continuum image is created by
averaging over all the line-free channels ($\nu_{\rm cont}\sim$90.7 GHz). This yields a synthesized clean beam size of 3\farcs5 $\times$ 3\farcs0 and an rms noise of 0.24 mJy beam$^{-1}$.

\subsection{VLA} 
Observations of the BLAH continuum ($\nu_{\rm rest}$ = BLAH GHz) toward the galaxy RXJ1131-1231 were carried out using the {\it Karl G. Jansky} Very Large Array (VLA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: BLAH; PI: BLAH).
Observations were carried out on BLAH under excellent/GOOD? BLAH mm weather conditions in the A array configurations. The C-Band receivers were used to cover the BLAH
, employing a correlator setup providing a bandwidth of BLAH GHz in each sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time after discarding unusable visibility data.

The nearby radio quasar BLAH was observed every BLAH minutes for
pointing, amplitude, and phase calibration, and BLAH was observed as the primary
absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding $\sim

@@

The AIPS package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
